---
title: "reprex"
author: "Allison Horst"
date: "8/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```

Your job is to identify an error, then make a reproducible example that would help future you or someone else understand how to write the code correctly. In other words, your reprex code will *work* and offer a solution to the error thrown in each of the following examples. 

Data are in `AS00601.csv` (and read in correctly below as `mack_creek_vertebrates`). 

Data package title: Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present

**Citation:** Gregory, S.V. and I. Arismendi. 2020. Aquatic Vertebrate Population Study in Mack Creek, Andrews Experimental Forest, 1987 to present ver 14. Environmental Data Initiative. https://doi.org/10.6073/pasta/7c78d662e847cdbe33584add8f809165

### Read in the data 

There are no problems here. 
```{r}
mack_creek_vertebrates <- read_csv(here("AS00601.csv"))
```

### reprex 1

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 1: 
mack_creek_lengths <- mack_creek_vertebrates %>% 
  clean_names() %>% 
  select(year:sampledate) %>% 
  filter(section == "CC") %>% 
  mutate(across(.cols = where(is.character), .fns = tolower)) %>% 
  drop_na(species) %>% 
  group_by(species) %>% 
  summarize(mean_length_cm = mean(length1, na.rm = TRUE),
            sd_length_cm = sd(length1, na.rm = TRUE)) %>% 
  ungroup()
```

```{r}
library(tidyverse)
library(here)
library(janitor)

df <- tribble(
  ~Name, ~Hike, ~Length,
  "Paloma", "SB", 40,
  "Halina", "VC", 15,
  "Mia", "TC", 25
)

df

df %>% 
  clean_names() %>% 
  mutate(across(.cols = where(is.character), .fns = tolower))

#To use the across function, make sure you specify your arguments are matched up with the correct columns (.cols) and functions (.fns). Also, make sure your parenthesis do not get mixed up as they can easily get lost in the mutation.
```

### reprex 2

Identify what is causing the problem in the code below (there's only one thing). Then, create a very simple reprex that would help yourself, future you, or a colleague fix the problem. **Post your reprex as an issue in your own fork on GitHub.**

```{r}
# Example 2:
mack_creek_vertebrates %>% 
  clean_names() %>% 
  filter(species == "ONCL") %>% 
  ggplot(aes(x = length1, y = weight)) +
         geom_point(shape = 12, color = "purple") +
         theme_minimal() +
         labs(x = "Cutthroat trout length (cm)",
              y = "Weight (g)")
```
```{r}
library(tidyverse)
library(palmerpenguins)

penguins %>% 
  filter(species == "Gentoo") %>% 
  ggplot(aes( x = body_mass_g, y = flipper_length_mm)) +
  geom_point(shape = 3, color = "red")

# When using the aes() within geom_point() you must connect it to a variable within the data frame. For the example above you could not do the following, geom_point(aes(shape = 3)), but you could do geom_ooint(aes(color = island)).
```

## End